\section{Background}
Obtaining a private pilot's license is one of the first steps in any commercial pilot's career, and often the end goal of any prospective private pilot.
The preparation and examination for such a qualification is often a very costly endeavour, mainly due to the need for frequent practice with qualified instructors.
Many students hence have to go into their examinations not feeling confident in their abilities.

One possible solution is for students to use an online practice system, alongside practice with qualified instructors. This helps reduce the high financial cost of obtaining a pilot's license and allows substantially more practice than would be available with just a human instructor.

The Coronavirus pandemic has increased the need for pilot refresher training, with the European Union Aviation Safety Agency (EASA) releasing guidelines on extra training for pilots and ground staff who are coming back from an extended break from work \cite{EASA-training-post-covid}. Given the nature of the flight profession, pilots may not be able to physically attend regular training if they are travelling, hence a system that offers online solo practice with no need for arranging an instructor could form part of a pilot's continued skills practice.
\section{Existing software}
Two online practice apps exist currently which provide students an experience close to that which they will encounter in the exam, Readability 5 \cite{readability5} and Wilco Radio \cite{wilcoradio}.
Both systems provide a simulated RTC which the student can communicate with via a text box or selecting from a provided set of options. This is a major limitation, and combined with the fact that scenarios come from a pool of predefined options, students can learn the correct responses to each scenario without actually understanding the underlying concepts. The limited set of scenarios could also leave students insufficiently practised. These flaws leave a gap in the market for a more comprehensive solution.